---
title: "QMM Module 9"
author: "Yash Bhanushali"
date: "06/11/2022"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Based on the problem statement, the goal is to:

Maximize Z = P - 6*C - 3*D

  P = total (discounted) profit over the life of the new products,
  C = change (in either direction) in the current level of employment,
  D = decrease (if any) in next year’s earnings from the current year’s level.

Subject to:

Total Profit: Maximize P = 20*X1 + 15*X2 + 25*X3

Employment Level: 6*X1 + 4*X2 + 5*X3 = 50

Earnings Next Year: 8*X1 + 7*X2 + 5*X3 >= 75

As a result, the auxillery variables become:

Y1 = 6*X1 + 4*X2 + 5*X3 - 50
Y2 = 8*X1 + 7*X2 + 5*X3 - 75

Which becomes:

(Y1P - Y1M) = 6*X1 + 4*X2 + 5*X3 - 50
(Y2P - Y2M) = 8*X1 + 7*X2 + 5*X3 - 75

Therefore, the final setup of the problem statement is:

Maximize Z = 20*X1 + 15*X2 + 25*X3 - 6*Y1P - 6*Y1M - 3*Y2M

Subject to:

6*X1 + 4*X2 + 5*X3 - (Y1P - Y1M) = 50
8*X1 + 7*X2 + 5*X3 - (Y2P - Y2M) = 75

And:

X1, X2, X3 >= 0
Y1P, Y1M, Y2P, Y2M >= 0

Lastly, we will run this problem in R as a linear programming model and discuss the results.

```{r}
# This problem will require the "lpSolveAPI" library
require(lpSolveAPI)
```


```{r}
#Set Working Directory
getwd()
setwd("D:/MSBA/QMM/Assignment module 9")

```

```{r}
# Import the .lp file for this problem
lpm <- read.lp(filename = "emax.lp", type = "lp")
# Return the linear programming model
lpm
```

```{r}
# Solve the linear programming model
solve(lpm)
get.objective(lpm)
get.variables(lpm)
```

Based on the output of the linear programming model, we can conclude several things.

X1 = 0
X2 = 0
X3 = 15
Y1P = 25
Y1M = 0
Y2M = 0
Y2P = 0

This leads us to the conclusion that only product 3 should be included in the product mix. A 225 unit object value would result from this combination. The employment level goal will be exceeded by 25 units, which translates to 2,500 employees and a penalty of 150 units to the objective function, while the profits goal for the upcoming year is fully satisfied.