---
title: "QMM Assignment 5 Module 8"
author: "YASH BHANUSHALI"
date: "2022-10-30"
output:
  word_document: default
  html_document: default
---



## Question 1 - Hope Valley Health Care Association

Problem Description -- The Hope Valley Health Care Association owns and operates six nursing homes in adjoining states. An evaluation of their efficiency has been undertaken using two inputs and two outputs. The inputs are staffing labor (measured in average hours per day) and the cost of supplies (in thousands of dollars per day). The outputs are the number of patient-days reimbursed by third-party sources and the number of patient-days reimbursed privately. A summary of performance data is shown in the table below.
```{r}
# This package is required for running the DEA functions in this program
require(Benchmarking)
```

Next, the problem data will be loaded into the R environment.

```{r}
# Create matrix for the two inputs
X <- matrix(c(150, 400, 320, 520, 350, 320, 0.2, 0.7, 1.2, 2.0, 1.2, 0.7), ncol = 2)
# Create matrix for the two outputs
Y <- matrix(c(14000, 14000, 42000, 28000, 19000, 14000, 3500, 21000, 10500, 42000, 25000, 15000), ncol = 2)
# Name the columns of the inputs and outputs
colnames(X) <- c("Staff Hours per Day","Supplies per Day")
colnames(Y) <- c("Reimburse Patient-Days", "Privately Paid Patient-Days")
# Return the matrices for review
print(X)
print(Y)
```

The results of DEA using the FDH method will be returned by the next chunch of code.

```{r}
# DEA code utilizing the FDH method
FDH <- rep("FDH", times = 6)
Not_Applicable <- rep(NA, times = 6)
DEA_FDH <- dea(X, Y, RTS = "FDH")
DEA_FDH_Peers <- peers(DEA_FDH)                             
DEA_FDH_Lambda <- lambda(DEA_FDH)  
print(DEA_FDH)
print(DEA_FDH_Peers)
print(DEA_FDH_Lambda)
dea.plot.isoquant(X, Y, RTS= "FDH")
# Summarize the results for addition to a summary table
DEA_FDH_Peers <- cbind(DEA_FDH_Peers, Not_Applicable, Not_Applicable)
FDH_Summary <- cbind(FDH, DEA_FDH$eff, DEA_FDH_Peers, DEA_FDH_Lambda)
colnames(FDH_Summary) <- c("Method","Eff", "P1", "P2", "P3", "L1", "L2", "L3", "L4", "L5", "L6")
print(FDH_Summary)
```

The results of DEA using the CRS method will be returned by the next chunch of code.

```{r}
# DEA code utilizing the CRS method
CRS <- rep("CRS", times = 6)
DEA_CRS <- dea(X, Y, RTS = "CRS")
DEA_CRS_Peers <- peers(DEA_CRS)                             
DEA_CRS_Lambda <- lambda(DEA_CRS)                            
print(DEA_CRS)
print(DEA_CRS_Peers)
print(DEA_CRS_Lambda)
dea.plot.isoquant(X, Y, RTS= "CRS")
# Summarize the results for addition to a summary table
DEA_CRS_Lambda <- cbind(DEA_CRS_Lambda, Not_Applicable, Not_Applicable)
CRS_Summary <- cbind(CRS, DEA_CRS$eff, DEA_CRS_Peers, DEA_CRS_Lambda)
colnames(CRS_Summary) <- c("Method","Eff", "P1", "P2", "P3", "L1", "L2", "L3", "L4", "L5", "L6")
CRS_Summary <- as.data.frame(CRS_Summary)
CRS_Summary
```

The results of DEA using the VRS method will be returned by the next chunch of code.

```{r}
# DEA code utilizing the VRS method
VRS <- rep("VRS", times = 6)
DEA_VRS <- dea(X, Y, RTS = "VRS")
DEA_VRS_Peers <- peers(DEA_VRS)                             
DEA_VRS_Lambda <- lambda(DEA_VRS)                            
print(DEA_VRS)
print(DEA_VRS_Peers)
print(DEA_VRS_Lambda)
dea.plot.isoquant(X, Y, RTS= "VRS")
# Summarize the results for addition to a summary table
DEA_VRS_Lambda <- cbind(DEA_VRS_Lambda, Not_Applicable)
VRS_Summary <- cbind(VRS, DEA_VRS$eff, DEA_VRS_Peers, DEA_VRS_Lambda)
colnames(VRS_Summary) <- c("Method","Eff", "P1", "P2", "P3", "L1", "L2", "L3", "L4", "L5", "L6")
VRS_Summary <- as.data.frame(VRS_Summary)
VRS_Summary
```

The results of DEA using the IRS approach will be returned by the next chunch of code.

```{r}
# DEA code utilizing the IRS method
IRS <- rep("IRS", times = 6)
DEA_IRS <- dea(X, Y, RTS = "IRS")
DEA_IRS_Peers <- peers(DEA_IRS)                             
DEA_IRS_Lambda <- lambda(DEA_IRS)                            
print(DEA_IRS)
print(DEA_IRS_Peers)
print(DEA_IRS_Lambda)
dea.plot.isoquant(X, Y, RTS= "IRS")
# Summarize the results for addition to a summary table
DEA_IRS_Lambda <- cbind(DEA_IRS_Lambda, Not_Applicable)
IRS_Summary <- cbind(IRS, DEA_IRS$eff, DEA_IRS_Peers, DEA_IRS_Lambda)
colnames(IRS_Summary) <- c("Method","Eff", "P1", "P2", "P3", "L1", "L2", "L3", "L4", "L5", "L6")
IRS_Summary <- as.data.frame(IRS_Summary)
IRS_Summary
```

The results of DEA using the DRS method will be returned by the next section of code.

```{r}
# DEA code utilizing the DRS method
DRS <- rep("DRS", times = 6)
DEA_DRS <- dea(X, Y, RTS = "DRS")
DEA_DRS_Peers <- peers(DEA_DRS)                             
DEA_DRS_Lambda <- lambda(DEA_DRS)                            
print(DEA_DRS)
print(DEA_DRS_Peers)
print(DEA_DRS_Lambda)
dea.plot.isoquant(X, Y, RTS= "DRS")
# Summarize the results for addition to a summary table
DEA_DRS_Lambda <- cbind(DEA_DRS_Lambda, Not_Applicable, Not_Applicable)
DRS_Summary <- cbind(DRS, DEA_DRS$eff, DEA_DRS_Peers, DEA_DRS_Lambda)
colnames(DRS_Summary) <- c("Method","Eff", "P1", "P2", "P3", "L1", "L2", "L3", "L4", "L5", "L6")
DRS_Summary <- as.data.frame(DRS_Summary)
DRS_Summary
```

The results of DEA using the FRH/ADD technique will be returned by the following chunch of code.

```{r}
# DEA code utilizing the ADD method
ADD <- rep("ADD", times = 6)
DEA_ADD <- dea(X, Y, RTS = "ADD")
DEA_ADD_Peers <- peers(DEA_ADD)                             
DEA_ADD_Lambda <- lambda(DEA_ADD)                            
print(DEA_ADD)
print(DEA_ADD_Peers)
print(DEA_ADD_Lambda)
# Summarize the results for addition to a summary table
DEA_ADD_Peers <- cbind(DEA_ADD_Peers, Not_Applicable, Not_Applicable)
ADD_Summary <- cbind(ADD, DEA_ADD$eff, DEA_ADD_Peers, DEA_ADD_Lambda)
colnames(ADD_Summary) <- c("Method","Eff", "P1", "P2", "P3", "L1", "L2", "L3", "L4", "L5", "L6")
ADD_Summary <- as.data.frame(ADD_Summary)
ADD_Summary
```

```{r}
# Combine all of the method summary tables into one large summary table for each method
Summary_Table <- rbind(FDH_Summary, CRS_Summary, VRS_Summary, IRS_Summary, DRS_Summary, ADD_Summary)
# Return the summary table for review
print(Summary_Table)
```

The summary table reveals that the FRH and FDH algorithms both return efficiency of 1.0, the same peer and lambda values, and this for all six DMUs. 
DMU[1:4] was discovered to be effective at 1.0 by the CRS approach. DMU[1:5] was discovered to be effective at 1.0 through the VRS approach. 
DMU[1:4] was shown to be efficient at 1.0 using the DRS technique and IRS, respectively. 
All of the less efficient DMUs had Peer[1] and Peer[2] values of 1 and 2, respectively; the Peer[3] value, however, varied depending on the method, being either 4 or 5. 
Furthermore, for the identical DMU, the relative weights (lambdas) for all approaches were rather close.
